\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis

### 2018-05-22 paper/ms.tex
using minted to display code; make the abstract readable in small screens

\begin{abstract}
The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects. These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet candidates. However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as aperture choice and background correction methods. These assumption are valid for the majority of targets, but for certain science cases a bespoke analysis may be needed. Performing custom photometry with the raw Kepler data has many benefits. Working with the raw data allows users to mitigate systematics for their particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline. Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic rays or identify stray asteroids in the target aperture. To this end, we present \lightkurve, an open source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve~ tools it is simple and quick to create corrected time-series photometry from raw pixel data from any of these missions and perform many common light curve corrections, including correcting for K2 motion using the SFF method. \lightkurve~ is open source and provides an excellent learning tool for any users wanting to get to started with Kepler data.
\end{abstract}

@@

A \LightCurve~object can be instantiated by passing a \texttt{time}
array, a \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
\begin{minted}{python}
>>> from lightkurve import LightCurve
>>> lc = LightCurve(time, flux)
\end{minted}

@@

Therefore, one can, for example, perform the following series of operations
in order to fold a lightcurve from the MAST archive
\begin{minted}{python}
>>> lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
>>> klc.plot()
\end{minted}

@@

\begin{verbatim}
>>> import numpy as np
>>> from lightkurve import KeplerTargetPixelFile
>>> tpf = KeplerTargetPixelFile("kplr008462852-2011073133259_lpd-targ.fits")
>>> tpf.plot()
>>> tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

@@

In \texttt{lightkurve}, the centroids in every cadence can be computed as
\begin{verbatim}
>>> from lightkurve import KeplerTargetPixelFile
>>> tpf = KeplerTargetPixelFile('ktwo246199087-c12_lpd-targ.fits.gz')
>>> x_star, y_star = tpf.get_centroids()
\end{verbatim}

@@

        \clh{If you want to include oktopus in this snippet you have to explain what it is to the reader:)}
        \begin{verbatim}
        >>> from lightkurve import KeplerTargetPixelFile
        >>> from lightkurve.psf import PRFPhotometry, SceneModel
        >>> from oktopus import UniformPrior
        >>> tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
        >>> prf = tpf.get_prf_model()
        >>> prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
        >>> scene = SceneModel(prf=[prfs])
        >>> phot = PRFPhotometry(scene_model=scene, prior=prior)
        >>> results = phot.fit(tpf.flux + tpf.flux_bkg)
        \end{verbatim}

@@

    \subsubsection{Correcting Spacecraft Motion using Lightkurve}
        Spacecraft-induced correlated noise remains one of the greatest hurdles to
        analyzing K2 lightcurves. Many algorithms have been developed to mitigate
        motion-dependent artifacts~\cite{vanderburg2014}[CITE K2SC and EVEREST].
        In \lightkurve, we implement an algorithm based off of the self-flat-field
        (SFF) presented in~\cite{vanderburg2014}.

@@

        \begin{verbatim}
        from lightkurve import KeplerTargetPixelFile
        tpf = KeplerTargetPixelFile("ktwo248667471-c14_lpd-targ.fits.gz")
        lc = tpf.to_lightcurve()
        centroids = tpf.get_centroids()
        lcc = lc.correct(centroids[0], centroids[1])
        \end{verbatim}

    \subsubsection{Correcting Common Systematics with CBVs using Lightkurve}

@@

        An example of SAP flux correction for target \texttt{KOI 8462852}
        (Tabby's star) can be written as follows
        \begin{verbatim}
        >>> from lightkurve.lightcurve import KeplerCBVCorrector
        >>> cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
        >>> cbv_lc = cbv.correct(cbvs=[1,2])
        \end{verbatim}

>>>>

\begin{abstract}
    The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects.
    These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet
    candidates. However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as
    aperture choice and background correction methods. These assumption are valid for the majority of targets,
    but for certain science cases a bespoke analysis may be needed. Performing custom photometry with the raw
    Kepler data has many benefits. Working with the raw data allows users to mitigate systematics for their
    particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline.
    Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic
    rays or identify stray asteroids in the target aperture. To this end, we present \lightkurve, an open
    source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface
    seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve~ tools it is
    simple and quick to create corrected time-series photometry from raw pixel data from any of these
    missions and perform many common light curve corrections, including correcting for K2 motion using
    the SFF method and correcting for correlated trends using cotrend basis vectors.
    \lightkurve~ is open source and provides an excellent learning tool for any users wanting
    to get to started with Kepler data.
\end{abstract}

@@

A \LightCurve~object can be instantiated by passing a \texttt{time}
array, a \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
\begin{minted}{python}
from lightkurve import LightCurve
lc = LightCurve(time, flux)
\end{minted}

@@

Therefore, one can, for example, perform the following series of operations
in order to fold a lightcurve from the MAST archive
\begin{minted}{python}
lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
klc.plot()
\end{minted}

@@

\begin{minted}{python}
import numpy as np
from lightkurve import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile("kplr008462852-2011073133259_lpd-targ.fits")
tpf.plot()
tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{minted}

@@

In \texttt{lightkurve}, the centroids in every cadence can be computed as
\begin{minted}{python}
from lightkurve import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile('ktwo246199087-c12_lpd-targ.fits.gz')
x_star, y_star = tpf.get_centroids()
\end{minted}

@@

        \clh{If you want to include oktopus in this snippet you have to explain what it is to the reader:)}
\begin{minted}{python}
from lightkurve import KeplerTargetPixelFile
from lightkurve.psf import PRFPhotometry, SceneModel
from oktopus import UniformPrior
tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
prf = tpf.get_prf_model()
prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
scene = SceneModel(prf=[prfs])
phot = PRFPhotometry(scene_model=scene, prior=prior)
results = phot.fit(tpf.flux + tpf.flux_bkg)
\end{minted}

@@

    \subsubsection{Correcting Spacecraft Motion}
        Spacecraft-induced correlated noise remains one of the greatest hurdles to
        analyzing K2 lightcurves. Many algorithms have been developed to mitigate
        motion-dependent artifacts~\cite{vanderburg2014}[CITE K2SC and EVEREST].
        In \lightkurve, we implement an algorithm based off of the self-flat-field
        (SFF) presented in~\cite{vanderburg2014}.

@@

\begin{minted}{python}
from lightkurve import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile("ktwo248667471-c14_lpd-targ.fits.gz")
lc = tpf.to_lightcurve()
centroids = tpf.get_centroids()
lcc = lc.correct(centroids[0], centroids[1])
\end{minted}

    \subsubsection{Correcting Common Systematics with CBVs}

@@

        An example of SAP flux correction for target \texttt{KOI 8462852}
        (Tabby's star) can be written as follows
\begin{minted}{python}
from lightkurve.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{minted}
